---
title: "CoolMolBio"
author: "s132347 (Sofie Emilie Hagelund), s253710 (Henrique Gomes), s253689 (Paula Meerjanssen), s252750 (Shuyue Zhang), s253719 (Eszter Hudra)"
output: rmarkdown::pdf_vignette
vignette: >
  %\VignetteIndexEntry{CoolMolBio}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

The package provides a collection of functions to perform basic functions on DNA sequences, like Translation, plotting etc. .

## Installation

load the library

```{r setup}
library(CoolMolBio)
```

## Functions

The packages has 5 different functions explained in the following:

### 1. dnaSequence()

This function generates a random DNA sequence of a specified length. It samples nucleotides ("A", "T", "G", "C") with replacement, meaning bases can repeat, and then concatenates them into a single string.

```{r}
dnaSequence(21)
```

### 2. DNA_to_RNA

This function receives a DNA strand as a string and converts all T's into U's, essentially turning it into an RNA strand. For example, the DNA strand "ATCTA" would become "AUCUA", while the strand "ACGCGA" would remain unchanged.

```{r}
DNA_to_RNA("ATCGCTAG")
```

### 3. extractCodon()

This function extracts codons from a DNA coding sequence. You can specify the starting nucleotide to shift the reading frame (default is 1). If the sequence length is not a multiple of 3, it extracts as many full codons as possible.

Extract codons from default coding frame:

```{r}
extractCodon("ATCGTC")
```

Extract codons starting from the second nucleotide:

```{r}
extractCodon("TATCGTC", 2)
```

### 4. translation()

The translation function converts mRNA codons into their a peptide sequence.

```{r}
translation(c("AUG", "GUC", "AUC"))
```

### 5. createHistogram()

This function generates a histogram that shows how often each nucleotide appears in a given DNA sequence. The output is a histogram where each bar represents one nucleotide.

```{r}
createHistogram("ATGCGTTA")
```
