---
title: "your_package_name"
author: "s132347(Sofie Emilie Hagelund), s253710(Henrique Gomes), s253689(Paula Meerjanssen), s252750(Shuyue Zhang), s253719(Eszter Hudra)"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{your_package_name}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<https://github.com/rforbiodatascience25/group_12_package.git>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

The package provides a collection of functions to perform basic functions on DNA sequences, like Translation, plotting etc. .

## Installation

```{r}
library(CoolMolBio)
devtools::load_all() #not sure if necessary
```

## Functions

The packages has 5 different functions explained in the following:

### Function 1

```{r}

```

### Function 2

```{r}

```

### Extract Codons from a Sequence
This function extracts codons from a DNA coding sequence. You can specify the starting nucleotide to shift the reading frame (default is 1).
Here are two examples:

```{r extractCodon_examples}
# Extract codons from default coding frame
extractCodon("ATCGTC")
#> [1] "ATC" "GTC"

# Extract codons starting from the second nucleotide
extractCodon("TATCGTC", 2)
#> [1] "ATC" "GTC"
```
The function returns a character vector of codons.
If the sequence length is not a multiple of 3, it extracts as many full codons as possible, igonring any remainder.
```{r}
extractCodon("ATCGT")
#> [1] "ATC"
```


### Function 4

```{r}

```

### createHistogram 

This function generates a histogram that shows how often each nucleotide appears in a given DNA sequence. The output is a histogram where each bar represents one nucleotide.

```{r}
createHistogram("ATGCGTTA")
```
