---
title: "Cool Mol Bio - Group 12"
author: "s132347(Sofie Emilie Hagelund), s253710(Henrique Gomes), s253689(Paula Meerjanssen), s252750(Shuyue Zhang), s253719(Eszter Hudra)"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{your_package_name}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<https://github.com/rforbiodatascience25/group_12_package.git>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

The package provides a collection of functions to perform basic functions on DNA sequences, like Translation, plotting etc. .

## Installation

installing the github

```{r}
devtools::install_github("rforbiodatascience25/group_12_package")
```

loading the library

```{r}
library(CoolMolBio)
```

Simulates library, us to use our functions

```{r}
devtools::load_all()
```

## Functions

The packages has 5 different functions explained in the following:

### Generate a DNA sequence of specified length

This function generates a random DNA sequence of a specified length. It samples nucleotides ("A", "T", "G", "C") with replacement, meaning bases can repeat, and then concatenates them into a single string. For example, with a sequence size of 9, the output could be "AATGCCGTA".

```{r}
dnaSequence <- function(dnaSize){
  dnaTmp <- sample(c("A", "T", "G", "C"), 
                   size = dnaSize, 
                   replace = TRUE)
  dna <- paste0(dnaTmp, 
                collapse = "")
  return(dna)
}
```

### DNA to RNA converter
This function receives a DNA strand as a string and converts all T's into U's, essentially turning it into an RNA strand. For example, the DNA strand "ATCTA" would become "AUCUA", while the strand "ACGCGA" would remain unchanged.

```{r}
DNA_to_RNA <- function(DNA_string){
  RNA_string <- gsub("T", "U", DNA_string)
  return(RNA_string)
}
```

### Extract Codons from a Sequence

This function extracts codons from a DNA coding sequence. You can specify the starting nucleotide to shift the reading frame (default is 1). Here are two examples:

```{r extractCodon_examples}
# Extract codons from default coding frame
extractCodon("ATCGTC")
#> [1] "ATC" "GTC"

# Extract codons starting from the second nucleotide
extractCodon("TATCGTC", 2)
#> [1] "ATC" "GTC"
```

The function returns a character vector of codons. If the sequence length is not a multiple of 3, it extracts as many full codons as possible, igonring any remainder.

```{r}
extractCodon("ATCGT")
#> [1] "ATC"
```

### Function 4

```{r}

```

### createHistogram()

This function generates a histogram that shows how often each nucleotide appears in a given DNA sequence. The output is a histogram where each bar represents one nucleotide.

```{r}
createHistogram("ATGCGTTA")
```
